# Unit 1 Title

## Overview

Welcome to [COURSE]

### Topics {.unnumbered}

This unit is divided into the following topics:
1.
2.
3.


### Unit Learning Outcomes {.unnumbered}

When you have completed this unit, you will be able to:

- Describe…
- Contrast…
- Analyze…
- Determine…
- Create…

### Learning Activities {.unnumbered}

Here is a list of learning activities that will benefit you in completing this unit. You may find it useful for planning your work.

::: {.learning-activity}

1. Read…
2. Watch…
3. Explore…
4. Complete the ungraded quiz.

*Note*: Working through course activities will help you to meet the learning outcomes and successfully complete your assessments.

:::

### Assessment {.unnumbered} 

Please see the Assessment section in Moodle for assignment details.

### Resources {.unnumbered}

Here are the resources you will need to complete this unit.

- (Textbook)
- Other online resources will be provided in the unit.

## Title for Topic 1

We begin Unit 1…

*(add content)*

### Activity: Title (e.g. Read, Reflect and View)

::: {.learning-activity time="00"}

*(add content)*

View the following resources about …

Next, watch the following videos that illustrate…

**Questions to Consider**

After completing the activities above, consider the following questions:

- This is a question?

:::

## Title for Topic 2

*(add content)*

### Activity: Title

::: {.learning-activity time="00"}

e.g. Case study

*(add content)*

::: {.note icon="true"}

Note that you may be asked to review this case or similar cases in your class discussion groups. You may want to prepare by relating the case to your readings. Specifically, identify the ethical issues and terms to help explain the case.

:::

:::

## Title for Topic 3

*(add content)*

…

### Activity: Title

::: {.learning-activity time="00"}

*(See [Assessment ideas](https://multi-access.twu.ca/assessment/assessment-ideas) for other ways to engage students in the topics.)*

:::

<!-- ### Activity: Key Terms Quiz (ungraded) {-}

::: {.learning-activity}

To review the concepts from this unit, take the following quiz.  This activity is ungraded and is designed to help prepare you for the assessments in this course.

Match the following terms to their correct definition.

1. **Term**– definition…
2. **Term**– definition…
3. **Term**– definition…

::: -->

## Summary {.unnumbered}

In this first unit, you have had the opportunity to learn about…

*(add content)*

::: check

Before you move on to the next unit, you may want to check that you are able to:

- Describe…
- Contrast…
- Analyze…
- Determine…
- Create…

:::

## References {.unnumbered}

## Practice Quiz {.unnumbered}

```{r, echo = FALSE, results='asis'}
knitr::opts_chunk$set(echo = FALSE)

# Uncomment to change widget colours:
# style_widgets(incorrect = "goldenrod", correct = "purple", highlight = "firebrick")
```

This is a Web Exercise template created by the [psychology teaching team at the University of Glasgow](http://www.psy.gla.ac.uk), based on ideas from [Software Carpentry](https://software-carpentry.org/lessons/). This template shows how instructors can easily create interactive web documents that students can use in self-guided learning.

The `{webexercises}` package provides a number of functions that you use in [inline R code](https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf) or through code chunk options to create HTML widgets (text boxes, pull down menus, buttons that reveal hidden content). Examples are given below. Render this file to HTML to see how it works.

**NOTE: To use the widgets in the compiled HTML file, you need to have a JavaScript-enabled browser.**

## Example Questions

### Fill-In-The-Blanks (`fitb()`)

Create fill-in-the-blank questions using `fitb()`, providing the answer as the first argument.

- 2 + 2 is `r fitb(4)`

You can also create these questions dynamically, using variables from your R session.

```{r}
x <- sample(2:8, 1)
```

- The square root of `r x^2` is: `r fitb(x)`

The blanks are case-sensitive; if you don't care about case, use the argument `ignore_case = TRUE`.

- What is the letter after D? `r fitb("E", ignore_case = TRUE)`

If you want to ignore differences in whitespace use, use the argument `ignore_ws = TRUE` (which is the default) and include spaces in your answer anywhere they could be acceptable.

- How do you load the tidyverse package? `r fitb(c("library( tidyverse )", "library( \"tidyverse\" )", "library( 'tidyverse' )"), ignore_ws = TRUE, width = "20")`

You can set more than one possible correct answer by setting the answers as a vector.

- Type a vowel: `r fitb(c("A", "E", "I", "O" , "U"), ignore_case = TRUE)`

You can use regular expressions to test answers against more complex rules.

- Type any 3 letters: `r fitb("^[a-zA-Z]{3}$", width = 3, regex = TRUE)`

### Multiple Choice (`mcq()`)

- "Never gonna give you up, never gonna: `r mcq(c("let you go", "turn you down", "run away", answer = "let you down"))`"
- "I `r mcq(c(answer = "bless the rains", "guess it rains", "sense the rain"))` down in Africa" -Toto

### True or False (`torf()`)

- True or False? You can permute values in a vector using `sample()`. `r torf(TRUE)`

### Longer MCQs (`longmcq()`)

When your answers are very long, sometimes a drop-down select box gets formatted oddly. You can use `longmcq()` to deal with this. Since the answers are long, It's probably best to set up the options inside an R chunk with `echo=FALSE`. 

**What is a p-value?**

```{r}
opts_p <- c(
   "the probability that the null hypothesis is true",
   answer = "the probability of the observed, or more extreme, data, under the assumption that the null-hypothesis is true",
   "the probability of making an error in your conclusion"
)
```

`r longmcq(opts_p)`

**What is true about a 95% confidence interval of the mean?**

```{r}
# use sample() to randomise the order
opts_ci <- sample(c(
  answer = "if you repeated the process many times, 95% of intervals calculated in this way contain the true mean",
  "there is a 95% probability that the true mean lies within this range",
  "95% of the data fall within this range"
))
```

`r longmcq(opts_ci)`

## Checked sections

Create sections with the class `webex-check` to add a button that hides feedback until it is pressed. Add the class `webex-box` to draw a box around the section (or use your own styles).

::: {.webex-check .webex-box}

I am going to learn a lot: `r torf(TRUE)`

```{r, results='asis'}
# statements
qs <- c(
  "My success is determined by my hard work and abilities.",
  "When I fail, it is usually because of external factors like bad luck or circumstances.",
  "I feel in control of the outcomes in my life.",
  "Good opportunities come to me because of my own efforts.",
  "Other people or events are often to blame when things don’t go as planned.",
  "I believe that my actions directly affect my future.",
  "Achieving my goals depends mostly on my decisions and persistence.",
  "Luck plays a significant role in determining whether I succeed or fail.",
  "I take full responsibility for the results of my decisions.",
  "External forces like the economy or other people have a big influence on my success."
)
rev_idx <- c(2, 5, 8, 10)  # reverse-scored items

# Likert labels; we name every option "answer" so webexercises marks it as selectable/correct,
# while the *score* comes only from the points vector we pass.
likert_labels <- c(
  "1 — Strongly Disagree",
  "2 — Disagree",
  "3 — Neutral",
  "4 — Agree",
  "5 — Strongly Agree"
)
likert_opts <- stats::setNames(likert_labels, rep("answer", length(likert_labels)))

# emit each item + longmcq with points
for (i in seq_along(qs)) {
  pts <- if (i %in% rev_idx) c(5,4,3,2,1) else 1:5
  cat(
    sprintf("<p><strong>%d.</strong> %s</p>\n", i, htmltools::htmlEscape(qs[i])),
    longmcq(likert_opts, points = pts),
    "<hr/>",
    sep = ""
  )
}

```

</div>

# Your Score
Total: <span id="locus-score">0</span> / <span id="locus-max">50</span><br/>
Interpretation: <span id="locus-interpretation">—</span>

:::


## Hidden solutions and hints

You can fence off a solution area that will be hidden behind a button using `hide()` before the solution and `unhide()` after, each as inline R code.  Pass the text you want to appear on the button to the `hide()` function.

If the solution is a code chunk, instead of using `hide()` and `unhide()`, simply set the `webex.hide` chunk option to TRUE, or set it to the string you wish to display on the button.

**Recreate the scatterplot below, using the built-in `cars` dataset.**

```{r}
with(cars, plot(speed, dist))
```


`r hide("I need a hint")`

See the documentation for `plot()` (`?plot`)

`r unhide()`

<!-- note: you could also just set webex.hide to TRUE -->

```{r, echo = TRUE, eval = FALSE}
#| webex.hide: "Click here to see the solution"
plot(cars$speed, cars$dist)
```
